---
title: "AGM minutes"
output: pdf_document
date: "`r Sys.Date()`"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      message = F,
                      warning = F)
```

**Members Present**

1. Maurice Ochieng

2. Cavin Wamache

3. Asha Sakina

4. Yvonne Atieno

5. Mercy Echessa

6. Dolphine Echessa

7. George Lukwiso

8. Violet Achieng'

9. Zamira Wakhu

10. Francis Olego

11. Diana Beatrice

12. Lawrence

**Preliminaries**

The meeting began at 2pm after members appointed Mr. Wamache Cavine to be the acting chairperson of the day. The opening prayer was offered by Echessa Mercy. The host welcomed members to their home. Members were given time to introduce themselves.

## Min 01/2025: 2025 Overview

The acting chairperson gave members present time to give their honest opinion about the events that occurred and how they were handled.
A member noted that our AGMs have no plans. She suggested that we need to plan for the AGMs early. She appreciated all who turned up.

It was noted that as an association, members need to think of an investment plan.
A member noted that welfare issues for 2025 were handled better, with ease compared to the previous years.

A member suggested that as an association we should avoid doing same things all the years. We need to find a way of encouraging savings by appreciating top savers.
A member emphasized that that the association was meant for bonding and catching up, visiting people's homes for AGMS should be maintained.

A member raised a concern on how one of the member's welfare and benevolent issues were handled. Members showed dissatisfaction on how it was handled and asked the leadership to step up and do better. Members were encouraged to use proper communication channels in case of a welfare issue.

## Min 02/2025: Way Forward

Members unanimously agreed that AGM venues should remain to remain to be family homes of members on rotational basis. It was agreed that the 2026 AGM would be held at Francis home. Members also agred that all subsequent AGMs would be held on 27th Dec of every year.

All members were encouraged to ensure availability during AGMs especially the officials.

**Budgeting for AGMs**

Due to the slight budgetary hitches during AGMs, it was suggested that:

1) Members to come up with a budget committee which should comprise of:

i) Secretary

ii) Treasurer

iii) Organising Secretary

iv) Welfare official

The following members were appointed as members of the budgeting committee:

i) Mercy Echessa

ii) Asha Sakina

iii) George Lukwiso

iv) Dolphine Echessa

The budgeting committee will come up with the budget to facilitate all the requirements of the AGMs.
Members agreed that during all AGMs, every member will be required to contribute Ksh. 1000 towards AGM so that the interest accrued from savings can be given back to the savers in the ratio of their contributions.

**Welfare communications**

Members agreed that all welfare communications should be made through the Chairperson, and then communicated to the main group for easy flow of information. Members were asked to avoid making welfare communications to the group without going through the Chairperson.

**Leadership**

Members were reminded that these are the current leaders:

1) Chairperson - Eric Odongo

2) Vice Chair - Janet Mukwabi

3) Treasurer - Asha Sakina

4) Secretary - Mercy Echessa

In addition, the following members were added:

1) George Lukwiso - Organizing Secretary

2) Dolphine Echessa - Welfare official

Members suggested that the term limit for each leadership body shall be a period of two years. This will give chance to every member to be a leader and serve the association. The current leaders will continue serving the organization until the next AGM in 2026 where new leaders will be elected.

## Min 3/2025: Financial Report

The treasurer gave the financial report as follows:

```{r}
library(knitr)
library(kableExtra)


tbl <- data.frame(
  Item = c("Registration fee","Seed Money","Total Savings",
           "Interest accrued"),
  Value = c("Ksh. 4,400","Ksh. 15,200","Ksh. 165,450","Ksh. 6,400")
  )

tbl |> 
  kable(caption = "Treasurer's Report")

kbl(tbl, booktabs = T) |> 
  kable_styling(full_width = T) |> 
  column_spec(1, width = "8cm")



```



The registration fee and interest accrued on savings were used to cater for the AGM budget.

Members whose seed money is less than Ksh. 1000 were asked to top up. Members agreed that seed money be retained by the treasurer for next years start up.

Members were asked to register as members for the year 2026. The registration fee remains Ksh. 200. The deadline for registration was agreed on as 30th January 2026.

## Min 4/2025: A.O.B

A new member joined the association. Members were happy and eager to welcome Lawrence to the association. Members were tasked to think of an investment plan.

## Min 5/2025: Adjournment

There being no any other business the meeting was adjourned at 4pm after a word of prayer from George, who also prayed for the meals. After swallowship, members left at their own pleasure.








